Tampering Detection In Low-Power \\ Smart Cameras

### 2015-06-21 paper.tex
ripassata sect 4

The most computationally demanding operations of Algorithm \ref{alg:DISPL} consists in computing of the indicators, in particular $g$. Assuming that $f_v$ and $f_h$ in~\eqref{eq:normaGradiente} are Sobel filters, this requires $34$ operations per pixels\footnote{Execution can be accelerated whether hardware implementations of the FFT transform are available}. Computing $l$ and $d$ requires 1 and 3 operations per pixel, respectively, while detecting outliers in the indicators requires two comparisons per frame. Thus, monitoring regions instead of the whole image has a negligible impact over the overall computational complexity. Algorithm~\ref{alg:DISPL} has a very low memory requirement: to compute $d$ it is necessary to store a single frame, while other indicators can be computed online. Segmentation is executed only during the initial configuration and can be performed on an external device connected to the smart camera. As such, Algorithm~\ref{alg:DISPL} can be properly executed on low-power and ultra low-power cameras.

%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}
\vspace{-0.2cm}
\section{Experiments}\label{sec:experiments}
Experiments are meant to assess the advantages of using a segmentation in a tampering-detection framework like Algorithm~\eqref{alg:DISPL}. In particular, to assess the importance of partitioning the scene we compare Algorithm~\eqref{alg:DISPL} against a solution monitoring the indicators on the whole image (\emph{Total} in Figure~\ref{fig:ROC}). To show that regions have to be defined depending on the image content, we consider also Algorithm~\eqref{alg:DISPL} when the $K$ regions are obtained by clustering $[r(x), c(x)]$, which yields a Voronoi partitioning of the scene (\emph{Voronoi} in Figure~\ref{fig:ROC}). For both regions defined as in Section~\ref{subsec:Segmentation} and Voronoi regions, we test the two extreme cases where $\Gamma_l = 1$ and $\Gamma_l = K-1$ ($\Gamma_d = 1$ and $\Gamma_d = K-1$).

\subsubsection{Datasets}
We recorded $8$ sequences from webcams monitoring different urban areas and we synthetically introduced $5\%$ of tampered frames in each. In each sequence we have cropped the central region, removing 50 rows from the top and bottom, and 50 columns from the left and right of the image. Blurring was obtained by convolution against a Gaussian kernels (as in Figure \ref{fig:sequences}(a)), while displacements were simulated by moving the central cropping regions of a random shift between 20 and 50 pixels in each direction (see Figure \ref{fig:sequences}(b)).  Overall, the dataset contains $24410$ frames, in which we've inserted $5\%$ of displacement events ($1224$ frames) and $5\%$ of blurring events ($1224$ frames).\footnote{Sequences can be released upon request.}
\gi{image sizes? blur kernel? quanti pixel il displacemnet?}
%The second dataset was recorded using a Raspberry Pi Model B+ \cite{raspberry} mounting a camera module.

%Few sequences of the first dataset contain real tampering events  (Figure \ref{fig:indicatori}). 
%In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens. 
\vspace{-0.3cm}
\subsubsection{Performance Assessment}
The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values. In particular, each point in the ROC curve depicts a pair of values (1-SPECIFICITY, RECALL) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP, FP, TN, FN represent the number of true positives (tampered frames correctly detected), of false positives (tampering-free frames detected), of true negatives (tampering-free frames not detected) and of false negatives (missed tampered frames), respectively, for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves and the Area Under the Curve (AUC) reported in Figure~\ref{fig:ROCdisplacement} and its caption indicate that camera displacements can be effectively detected by all the considered methods, and that Algorithm~\ref{alg:DISPL} achieves the best performance (the \emph{Frame-Difference} curve has not been reported because it was quite below the others). This result suggests that separately monitoring the luma over image regions is an effective strategy and that the regions have to be suitably estimated. For the visualization sake, these ROC curves have been reported in a limited range of both axis, and in particular we focus on low values of 1-SPECIFICITY, thus of false alarms. We observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.3\%$ of false alarms, which is half of the whole image solution ($0.7\%$) and less than one third of the Voronoi solution ($1\%$). Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.

In contrast, Figure~\ref{fig:ROCdefocus} confirms that when monitoring $g$ it is more convenient to consider the whole scene at once, as typically the regions $\{R_k\}$ do not include the most prominent edge of the scene, which are indeed the most informative part to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/curve}
\caption{\textbf{(a)} ROC curve for displacement detection.
	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
	The AUC corresponding to Algorithm~\ref{alg:DISPL} (Luma-Region) is $99.94\%$, the AUC of Luma-Total is $99.89\%$ the AUC of Luma-Voronoi is $99.85\%$, and the AUC of Frame-Difference is $99.44\%$ (axis have been zoomed for the visualization sake). Large AUC values indicate that these displacements can be successfully detected and that Algorithm~\ref{alg:DISPL} is the most effective one.
	\textbf{(b)} ROC curve for blurring detection.
	In this case, the Gradient-Total (AUC $99.96\%$) outperforms the Gradient-Regions (AUC $98.95\%$) because this latter do not include the most prominent edges in images, which are the most important information to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}

>>>>

The most computationally demanding operations of Algorithm \ref{alg:DISPL} consist in computing of the indicators, in particular $g$. Computing $g$ requires, when using the Sobel filters in~\eqref{eq:normaGradiente}, $34$ operations per pixels\footnote{Execution can be accelerated whether hardware implementations of the FFT transform are available}, while computing $l$ and $d$ requires 1 and 3 operations per pixel, respectively. Detecting outliers in the indicators requires two comparisons per frame: thus, monitoring regions instead of the whole image has a negligible impact on the overall computational complexity. Algorithm~\ref{alg:DISPL} has very low memory requirements: $l$ and $g$ indicators can be computed online, while $d$ requires to store a single frame in memory. Segmentation is executed only during the initial configuration and can be performed on an external device connected to the smart camera. As such, Algorithm~\ref{alg:DISPL} can be properly executed on low-power and ultra low-power cameras.

%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}
\vspace{-0.2cm}
\section{Experiments}\label{sec:experiments}
Experiments are meant to assess the advantages of using a segmentation in a tampering-detection framework like Algorithm~\eqref{alg:DISPL}. In particular, to assess the importance of partitioning the scene, we compare Algorithm~\eqref{alg:DISPL} against a solution monitoring the indicators on the whole image (\emph{Total} in Figure~\ref{fig:ROC}). To show that regions have to follow the image content, we consider Algorithm~\eqref{alg:DISPL} when the $K$ regions are obtained by clustering $[r(x), c(x)]$, which yields a Voronoi partitioning of the scene (\emph{Voronoi} in Figure~\ref{fig:ROC}). For both regions defined as in Section~\ref{subsec:Segmentation} and Voronoi regions, we test the two extreme cases where $\Gamma_l = 1$ and $\Gamma_l = K-1$ (respectively, $\Gamma_d = 1$ and $\Gamma_d = K-1$).

\subsubsection{Datasets}
We recorded $8$ sequences from webcams monitoring different urban areas and we synthetically introduced $5\%$ of tampered frames in each. In each sequence we have cropped the central region, removing 50 rows from the top and bottom, and 50 columns from the left and right of the image. Blurring was obtained by convolution against a Gaussian kernel (as in Figure \ref{fig:sequences}(a)), while displacements were simulated by moving the central cropping regions of a random shift between 20 and 50 pixels in each direction (see Figure \ref{fig:sequences}(b)).  Overall, the dataset contains $24410$ frames, in which we inserted $1224$ displacement frames ($5\%$) and $1224$ blurry frames ($5\%$)\footnote{Sequences can be released upon request.}.
\gi{Adriano: image sizes? blur kernel std? quanti pixel il displacement?}
%The second dataset was recorded using a Raspberry Pi Model B+ \cite{raspberry} mounting a camera module.

%Few sequences of the first dataset contain real tampering events  (Figure \ref{fig:indicatori}). 
%In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens. 
\vspace{-0.3cm}
\subsubsection{Performance Assessment}
The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values \gi{quale?}. In particular, each point in the ROC curve report a pair of values (1-SPECIFICITY, RECALL) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROCdisplacement} and the corresponding values of Area Under the Curve (AUC) reported in the caption, indicate that camera displacements can be effectively detected by all the considered methods, and that Algorithm~\ref{alg:DISPL} achieves the best performance when $\Gamma_l = \Gamma_d = 1$. This result suggests that separately monitoring the luma over image regions is an effective strategy and that the regions have to be suitably estimated.

\emph{We observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.3\%$ of false alarms, which is half of the whole image solution ($0.7\%$) and less than one third of the Voronoi solution ($1\%$). Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}
In contrast, Figure~\ref{fig:ROC}(c) confirms that when monitoring $g$ it is more convenient to consider the whole scene at once, as typically the regions $\{R_k\}$ do not include the most prominent edge of the scene, which are indeed the most informative part to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/curve}
\caption{\textbf{(a)} ROC curve for displacement detection.
	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
	The AUC corresponding to Algorithm~\ref{alg:DISPL} (Luma-Region) is $99.94\%$, the AUC of Luma-Total is $99.89\%$ the AUC of Luma-Voronoi is $99.85\%$, and the AUC of Frame-Difference is $99.44\%$ (axis have been zoomed for the visualization sake). Large AUC values indicate that these displacements can be successfully detected and that Algorithm~\ref{alg:DISPL} is the most effective one.
	\textbf{(b)} ROC curve for blurring detection.
	In this case, the Gradient-Total (AUC $99.96\%$) outperforms the Gradient-Regions (AUC $98.95\%$) because this latter do not include the most prominent edges in images, which are the most important information to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image. 
	\textbf{TODO} For the visualization sake, these ROC curves have been reported in a limited range of both axis, and in particular we focus on low values of 1-SPECIFICITY, thus of false alarms.
	}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}
